Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-09-19 GWLDCII.tex
some edits while talking

Specifically with $V$ and $W$ as in Lemma~\ref{lem I} and with $n-2, n-1\in I_{n-2}^V$ (so we are necessarily in Case 2 and $n-1$ supports at least one additional propagator) we have
  \begin{equation}\label{eq necklace}
  I_{n-3}^{V} \xrightarrow[\substack{n-3\text{ out}\\n-2\text{ in}}]{} I_{n-2}^{V} \xrightarrow[\substack{n-2\text{ out}\\n-5\text{ in}}]{} I_{n-1}^{V} \xrightarrow[\substack{n-1\text{ out}\\\text{something in}}]{} I_{n}^{V}  \xrightarrow[\substack{n \text{ out}\\\text{something in}}]{} I_1^{V}
  \end{equation}
  \note{Check: if we no longer need the $a,b$ in Figure \ref{fig messy}, we can probably rename these ``somethings'' to $a,b$ here.}
  where the first two transitions follow by the cyclic intervals property highlighted in Remark~\ref{rmk cyclic} along with the fact that $n-3$ is a supporting vertex in $V$.  The third transition follows from the definition of Grassmann necklaces and the fact that $n-1\in I_{n-2}^V$ by hypothesis, while the final transition follows from the fact that $n-1$ supports an additional propagator so we are guaranteed $n \in I_n^V$.

Note that neither ``something'' can be $n-1$, $n-2$, or $n-3$, because as noted in Lemma~\ref{lem I} these elements do not belong to $I_1^V$.

\note{Two versions of the same argument follow:}
The first ``something'' also cannot be $n-4$, for the following reason. By Remark~\ref{rmk cyclic} we know that $I_{n-1}^W(q) = n-5$, leaving no propagators supported on $n-4$ for $I_{n-1}^W$ to assign. Thus $n-4 \not\in I_{n-1}^W$, and since $I_{n-1}^W = I_n^V\cup\{n-1\}$ by Lemma~\ref{lem I}, we cannot have $n-4$ in $I_n^V$ either.

The first ``something'' also cannot be $n-4$, for the following reason. By Remark~\ref{rmk cyclic} we know that $I_{n-1}$ assigns $q$ to $n-5$ in both $V$ and $W$, so the only way we could have $n-4 \in I_n^V$ is if $I_n^V(q) = n-4$. By Lemma~\ref{lem I} this would imply $n-4 \in I_{n-1}^W$ as well, but since $I_{n-1}^W(q) = n-5$ there can be no propagators remaining when the algorithm reaches $n-4$.

However, it will be important later to observe that the second ``something'' could be $n-4$.

>>>>

Specifically with $V$ and $W$ as in Lemma~\ref{lem I} and with $n-2, n-1\in I_{n-2}^V$ (so we are necessarily in Case 2 and $n-1$ supports at least one additional propagator) we have
  \begin{equation}\label{eq necklace}
  I_{n-3}^{V} \xrightarrow[\substack{n-3\text{ out}\\n-2\text{ in}}]{} I_{n-2}^{V} \xrightarrow[\substack{n-2\text{ out}\\n-5\text{ in}}]{} I_{n-1}^{V} \xrightarrow[\substack{n-1\text{ out}\\ u \text{ in}}]{} I_{n}^{V}  \xrightarrow[\substack{n \text{ out}\\v \text{ in}}]{} I_1^{V}
  \end{equation}
where $u$ and $v$ are two vertices; we will derive some properties of them below.

The first two transitions follow by the cyclic intervals property highlighted in Remark~\ref{rmk cyclic} along with the fact that $n-3$ is a supporting vertex in $V$.  The third transition follows from the definition of Grassmann necklaces and the fact that $n-1\in I_{n-2}^V$ by hypothesis, while the final transition follows from the fact that $n-1$ supports an additional propagator so we are guaranteed $n \in I_n^V$.

Note that neither $u$ nor $v$ can be $n-1$, $n-2$, or $n-3$, because as noted in Lemma~\ref{lem I} these elements do not belong to $I_1^V$ and $I_n^V = (I_1^V\setminus \{v\}) \cup \{n\}$. However, $u$ could be $n$.

Also $u$ cannot be $n-4$, for the following reason. By Remark~\ref{rmk cyclic} we know that $I_{n-1}^W(q) = n-5$, leaving no propagators supported on $n-4$ for $I_{n-1}^W$ to assign. Thus $n-4 \not\in I_{n-1}^W$, and since $I_{n-1}^W = I_n^V\cup\{n-1\}$ by Lemma~\ref{lem I}, we cannot have $n-4$ in $I_n^V$ either.

However, it will be important later to observe that $v$ could be $n-4$.
